Outdated and License-Violating Code on Stack Overflow

### 2017-02-26 cloneoverflow-latex/cloneoverflow.tex
Checked the latest changes and corrected the bibliography.

A motivating example of outdated online code clones can be found in an
answer to a Stack Overflow question regarding how to implement
{\small{\texttt{RawComparator}}} in
\textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22262310}}.
\Cref{fig:before-after} shows a code snippet embedded as a part of the
accepted answer on the left. The snippet shows how \textsf{hadoop}
implements the {\small{\texttt{compare}}} method in its
{\small{\texttt{WritableComparator}}} class. The code snippet on the
right shows another version of the same method, but at this time
extracted from the latest version (as of 26 September 2016) of
\textsf{hadoop}. We can see that they are highly similar except a line
containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in
the latest version. The added line is intended for cleaning up the
reference in the {\small{\verb|buffer|}} variable. While this change
has already been introduced into the {\small{\texttt{compare}}} method
in the latest version of \textsf{hadoop}, the code example in Stack
Overflow post is still unchanged. This example shows that
inconsistencies between online code clones and their originals can
lead users of Stack Overflow to reuse outdated code.
%The code snippet on Stack Overflow can be outdated. %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

@@

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. 
% The archived dump has a size of 9 gigabytes. 
The data
dump is in XML format containing information of posts
(questions and answers) and 
% supporting data such as user accounts and timestamps of the posts.
we were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,332,940
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}} of Java source code.
Median of the snippet size is 10.
% excluding comments and blank lines.

\textbf{Open source systems: }
We selected the established \textbf{Qualitas} corpus~\cite{QualitasCorpus} 
for this study. It is a curated Java corpus that has been used in several
software engineering
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The
projects in the corpus represent various domains of software systems
ranging from programming languages to
visualisation. We selected the 20130901r release
of the Qualitas corpus containing 112 Java open source projects. This
release contains projects with releases no later than 1st September
2013. We intentionally chose an old corpus from 2013 since we are interested in
online code clones in the direction from open source projects to Stack
Overflow. The 20130901r snapshot provides Java code that is more than
2 years older than the Stack Overflow snapshot, which is sufficiently
long for a number of code snippets to be copied onto Stack Overflow
and also to observe if clones become outdated. Out of 112 Qualitas
projects, there is one project, \textsf{jre}, that does not contain
Java source code due to its licensing limitation~\cite{QualitasCorpus}
and is removed from the study. This resulted in a total of 111
projects analysed in the study. As shown in \Cref{tab:datasets}, the
111 Qualitas project have 166,709 Java files containing 19,614,083
lines of code. Median of the project size is 60,667 lines of code.

>>>>

A motivating example of outdated online code clones can be found in an
answer to a Stack Overflow question regarding how to implement
{\small{\texttt{RawComparator}}} in
\textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22262310}}.
\Cref{fig:before-after} shows a code snippet embedded as a part of the
accepted answer on the left. The snippet shows how \textsf{hadoop}
implements the {\small{\texttt{compare}}} method in its
{\small{\texttt{WritableComparator}}} class. The code snippet on the
right shows another version of the same method, but at this time
extracted from the latest version (as of 26 September 2016) of
\textsf{hadoop}. We can see that they both are highly similar except a line
containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in
the latest version. The added line is intended for cleaning up the
reference in the {\small{\verb|buffer|}} variable. While this change
has already been introduced into the {\small{\texttt{compare}}} method
in the latest version of \textsf{hadoop}, the code example in Stack
Overflow post is still unchanged. This example shows that
inconsistencies between online code clones and their originals can
lead users of Stack Overflow to reuse outdated code.
%The code snippet on Stack Overflow can be outdated. %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

@@

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. 
% The archived dump has a size of 9 gigabytes. 
The data
dump is in XML format containing information of posts
(questions and answers) and 
% supporting data such as user accounts and timestamps of the posts.
we were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,332,940
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}} of Java source code.
The median of the snippet size is 10.
% excluding comments and blank lines.

\textbf{Open source systems: }
We selected the established \textbf{Qualitas} corpus~\cite{QualitasCorpus} 
for this study. It is a curated Java corpus that has been used in several
software engineering
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The
projects in the corpus represent various domains of software systems
ranging from programming languages to
visualisation. We selected the 20130901r release
of the Qualitas corpus containing 112 Java open source projects. This
release contains projects with releases no later than 1st September
2013. We intentionally chose an old corpus from 2013 since we are interested in
online code clones in the direction from open source projects to Stack
Overflow. The 20130901r snapshot provides Java code that is more than
2 years older than the Stack Overflow snapshot, which is sufficiently
long for a number of code snippets to be copied onto Stack Overflow
and also to observe if clones become outdated. Out of 112 Qualitas
projects, there is one project, \textsf{jre}, that does not contain
Java source code due to its licensing limitation~\cite{QualitasCorpus}
and is removed from the study. This resulted in a total of 111
projects analysed in the study. As shown in \Cref{tab:datasets}, the
111 Qualitas project have 166,709 Java files containing 19,614,083
lines of code. The median project size is 60,667 lines of code.
